Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-12-18 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
add note for justifying x=50km sample line

At $\Delta z = \SI{300}{\meter}$, vertical velocities on the BTF and cut cell grids are visually indistinguishable (not shown).  They agree with the high resolution mass-conserving semi-implicit semi-Lagrangian solution from \citet{melvin2010}.
The initial thermal profile is subtracted from the potential temperature field at the end of the integration to reveal the structure of thermal anomalies.  The anomalies on the BTF grid with $\Delta z = \SI{50}{\meter}$ is shown in figure~\ref{fig:gw-theta}.  A vertical profile is taken at $x = \SI{50}{\kilo\meter}$, marked by the dashed line in figure~\ref{fig:gw-theta}, with results shown for the BTF grids in figure~\ref{fig:gw-sampleLine}a and on the cut cell grids in figure~\ref{fig:gw-sampleLine}b.  On all grids, potential temperature differences increase with height in the lowest \SI{1200}{\meter} at $x = \SI{50}{\kilo\meter}$, in agreement with the results seen in figure~\ref{fig:gw-theta}.  Results are seen to converge on all grids, with the exception of small errors in the lowest layers on the cut cell grids.

>>>>

At $\Delta z = \SI{300}{\meter}$, vertical velocities on the BTF and cut cell grids are visually indistinguishable (not shown).  They agree with the high resolution mass-conserving semi-implicit semi-Lagrangian solution from \citet{melvin2010}.
The initial thermal profile is subtracted from the potential temperature field at the end of the integration to reveal the structure of thermal anomalies.  The anomalies on the BTF grid with $\Delta z = \SI{50}{\meter}$ is shown in figure~\ref{fig:gw-theta}.  A vertical profile is taken at $x = \SI{50}{\kilo\meter}$, marked by the dashed line in figure~\ref{fig:gw-theta}, with results shown for the BTF grids in figure~\ref{fig:gw-sampleLine}a and on the cut cell grids in figure~\ref{fig:gw-sampleLine}b.
\TODO{say why x=50km is a good place to take these measurements.}
On all grids, potential temperature differences increase with height in the lowest \SI{1200}{\meter} at $x = \SI{50}{\kilo\meter}$, in agreement with the results seen in figure~\ref{fig:gw-theta}.  Results are seen to converge on all grids, with the exception of small errors in the lowest layers on the cut cell grids.
